Insights Into Computational Reproducibility in Plant Pathology and a Way Forward

### 2021-06-14 analysis/paper/paper.Rmd
clarify priors
comment out last line of author contributions until have feedback from all

Relatively flat priors were selected with a mean 0 and a standard deviation 10 for the fixed effects.

@@

# Authors' contributions
A.H.S, E.DP, Z.F. and N.J.G. conceived of the presented idea and scoring system.
N.J.G. provided five-year impact factors.
A.H.S, E.DP, Z.F. and K.dSA evaluated articles for scoring.
A.H.S. designed the computational framework with feedback from E.DP and Z.F.
A.H.S wrote the manuscript in consultation with E.DP.
All authors provided critical feedback and helped contribute to the final version of the manuscript.

>>>>

Relatively flat priors were selected with a mean of 0 and a standard deviation of 10 for the fixed effects.

@@

# Authors' contributions

A.H.S, E.DP, Z.F. and N.J.G. conceived of the presented idea and scoring system.
N.J.G. provided five-year impact factors.
A.H.S, E.DP, Z.F. and K.dSA evaluated articles for scoring.
A.H.S. designed the computational framework with feedback from E.DP and Z.F.
A.H.S wrote the manuscript in consultation with E.DP.
<!-- All authors provided critical feedback and helped contribute to the final version of the manuscript. -->
